### 2018-08-13 doc/plos/text/manuscript.tex
add ablation experiments

@@

>>>>

\subsubsection*{Sensitivity to each data source}

Digital surveillance is intermittent by nature, and data sources are subject to
sporadic, periodic (e.g. EPIC), and permanent (e.g. GFT) periods of
absence. We expect sensor fusion to gracefully handle these cases, but it is
not immediately clear what impact the absence of a given data source has on the
quality of the resulting nowcast.

To explore this question, we compare accuracy of nowcasts with and without each
data source in a set of eight ``ablation'' experiments in
Fig~\ref{figure_accuracy_vs_ablation}. For a given data source, we compute the
US national nowcast with and without that source and compare error in terms of
MAE and RMSE. Since the difficulty of nowcasting varies over time, we restrict
these comparisons to the set of weeks on which a particular data source (or,
more accurately, its fitted sensors) are available.

\begin{figure}[!ht]
  \maybeincludegraphics{accuracy_vs_ablation}
  \caption{
    {\bf Nowcast error compared with and without each data source.}
    TODO: explain this
  }
  \label{figure_accuracy_vs_ablation}
\end{figure}

As expected, we generally find that removal of a particular data source causes
an increase (or, in the case of WIKI, no meaningful change) in nowcasting
error. However, there are a couple of exceptions: TWTR and CDC. Nowcasting
error \textit{decreases} when removing these data sources. This is unexpected
in theory and strongly suggests violated assumptions (e.g. the relationship of
these sources with wILI may be nonlinear) or overfitting (e.g. covariance may
be underestimated for these sources).

\subsubsection*{Sensitivity to geographic resolution}

TODO(abscission experiments)

@@

TODO(curse of dimensionality and regularization)

TODO(ablation: overfitting, assumptions, time-variable relationships)
